A Study of Target Following with X-Ray Vision in Augmented Reality

### 2009-06-25 Paper/paper.tex

The parameters of our experiment are divided between the ``real'' immersion factors, such as the field of view of the HMD, and the ``augmented'' immersion factors, such as the field of view of the simulated AR display, and the performance of the tracking sensor.  We introduce periods of sensor dropouts, where the augmented overlays disappear, to simulate the effect of dropouts in a real tracking system.  For example, such dropouts might occur with a magnetic sensor near interfering material.

>>>>

The parameters of our experiment are divided between the ``real'' components of immersion, such as the field of view of the HMD, and the ``augmented'' components of immersion, such as the field of view of the simulated AR display, and the performance of the tracking sensor.  We introduce periods of sensor dropouts, where the augmented overlays disappear, to simulate the effect of dropouts in a real tracking system.  For example, such dropouts might occur with a magnetic sensor near interfering material.
